Supplementary Files

### 2018-01-20 Source/Supplementary_Files/supplementary_files.Rmd
Update README file, parameters file, and codes for supplementary files

```{r}
library(RCy3)
library(plyr)
library(dplyr)
library(RODBC)
library(sqldf)
library(knitr) # required for the 'kable' function for printing pretty table in html

@@

@@

## Helper Codes: Build phenotype master table 
```{r}

@@

## Table S9. The list of all the triplets in the filtered integrated network and triplets with genes that are cell cycle-regulated, essential and toxic on overexpression, and their shared phenotype on knockout and GO slim terms.
```{r}

@@

 # Protein interaction network
  # Number of interactions
 sbi_interactome %>%
     dplyr::select (one_of(c("oln_id_a", "oln_id_b"))) %>%
     dplyr::filter( oln_id_a > oln_id_b) %>%
     dplyr::distinct()%>%
     dplyr::count()

  # Number of proteins
 c( sbi_interactome [, "oln_id_a"], sbi_interactome [, "oln_id_b"] ) %>% unique() %>% length()

@@

# Total Number of Interactions (Unique Pairs of Proteins)
interactions_combined %>%
  dplyr::select (one_of(c("oln_id_a", "oln_id_b"))) %>%
  dplyr::filter (oln_id_a > oln_id_b) %>%
  dplyr::distinct()%>%
  dplyr::count()

@@

# Total Number of Interactions (Non-unique pairs and direction)
interactions_combined %>%
  dplyr::select (one_of(c("oln_id_a", "oln_id_b"))) %>%
  dplyr::filter (oln_id_a > oln_id_b) %>%
  dplyr::count()

@@

>>>>

## Import Libraries
```{r}
library(RCy3)
library(plyr)
library(dplyr)
library(RODBC)
library(sqldf)
library(knitr) # required for the 'kable' function for printing pretty table in html

@@

## Codes for Supplementary Figures S1-4 can be found in the following file: Source/Figures/paper_figures.Rmd

@@

## Supplementary Table S5: Build phenotype master table 
```{r}

@@

## Supplementary Table S9. The list of all the triplets in the filtered integrated network and triplets with genes that are cell cycle-regulated, essential and toxic on overexpression, and their shared phenotype on knockout and GO slim terms.
```{r}

@@

 # Protein interaction network
  # Number of interactions
 sbi_interactome_collated %>%
     dplyr::select (one_of(c("oln_id_a", "oln_id_b"))) %>%
     dplyr::filter( oln_id_a >= oln_id_b) %>%
     dplyr::distinct()%>%
     dplyr::count()

  # Number of proteins
 c( sbi_interactome_collated [, "oln_id_a"][[1]], sbi_interactome_collated [, "oln_id_b"][[1]] ) %>% unique() %>% length()

@@

# Total Number of Interactions (Unique Pairs of Proteins)
  interactions_combined_a <- interactions_combined %>%
                            dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b")))

  interactions_combined_b <- interactions_combined %>%
                            dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b"))) %>%
              							dplyr::rename( temp=oln_id_a) %>%
              							dplyr::rename( oln_id_a=oln_id_b) %>%
                            dplyr::rename( oln_id_b=temp)

  unique_interactions_combined <- dplyr::union  (interactions_combined_a, interactions_combined_b ) %>%
					dplyr::distinct()  %>%
				  dplyr::filter( oln_id_a >= oln_id_b )

 unique_interactions_combined %>%
  dplyr::select (one_of(c("oln_id_a", "oln_id_b"))) %>%
  dplyr::distinct() %>%
  dplyr::count()

@@

# Total Number of Interactions (Non-unique pairs and direction)
interactions_combined %>%
  dplyr::select (one_of(c("oln_id_a", "oln_id_b", "interaction_type_abbrev"))) %>%
  dplyr::filter (oln_id_a >= oln_id_b) %>%
    dplyr::filter ( !(oln_id_a == oln_id_b & interaction_type_abbrev == "tu") ) %>%
    dplyr::filter ( !(oln_id_a == oln_id_b & interaction_type_abbrev == "ku") ) %>%
  dplyr::distinct() %>%
  dplyr::count()

@@

## Supplementary Table S10
Results for Supplementary Table S10 can be found in the following file: Results/Bootstrap_p_values/Negative_Genetic_Interactions/Final_Results/full_results_triplet_motifs_costanzo_2016_collated.tab

## Supplementary Table S11
Codes for Supplementary Table S11 can be found in the following R Notebook (in the same directory as this script): Source/Supplementary_Files/percentage_of_network_analyzed.Rmd
